6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Layout and wording tweaks

In this report, we discuss and implement an infrastructure modelling and monitoring tool that can be used to help manage some of the inherent complexity in modern infrastructure. The emphasis of this investigation is on small to medium size software deployments, where significant resources are not typically invested into solving these issues.

\chapter*{Originality Avowal}
I verify that I am the sole author of this report, except where explicitly stated to the contrary. I grant the right to King’s College London to make paper and electronic copies of the submitted work for purposes of marking, plagiarism detection and archival, and to upload a copy of the work to Turnitin or another trusted plagiarism detection service. I confirm this report does not exceed 25,000 words.

@@

I would like to express my gratitude to Dr.\ Steffen Zschaler, for agreeing to supervise this project when it was a rather abstract idea, and his subsequent useful advice throughout the year.

@@

\pagebreak
\subsection{Unit and Integration Testing}

@@

\begin{listing}[h]
\begin{minted}[fontfamily=fi4]{ruby}
class sshd {
    package { 'openssh-server':
        ensure => latest
    }
    service { 'ssh':
        subscribe => File[sshdconfig],
        require   => Package['openssh-server'],
    }
    file { 'sshdconfig': 
        name    => '/etc/ssh/sshd_config',
        owner   => root,
        group   => root,
        mode    => 644,
        source  => 'puppet:///sshd/sshd_config',
        require => Package['openssh-server'],
    }
}
\end{minted}
\caption{A puppet recipe snippet, declaratively configuring the SSH service on a host. The execution of this description is idempotent, so can be repeated safely to ensure convergence.}
\label{fig:PuppetDSLSnippet}
\end{listing}

@@

Whilst New Relic is extremely simple to set up and provides a fairly deep insight into application performance, it is a relatively expensive service beyond a trivial number of hosts, treats all hosts as independent nodes rather than interconnected services with dependencies, and lacks the extensibility of the open source solutions when it comes to monitoring other non-supported parts of the stack.

@@

\pagebreak
\section{Appendix}
\subsection{Service Specification Examples}
\label{dslexamples}

\subsubsection{X-Time}
\label{dslgem}
\inputminted[fontfamily=fi4]{ruby}{appendices/x-time.rb}

\subsubsection{X-Awards Site}
\inputminted[fontfamily=fi4]{ruby}{appendices/x-awards-site.rb}

\subsubsection{Workspace +}
\inputminted[fontfamily=fi4]{ruby}{appendices/workspace.rb}

>>>>

In this report, we discuss and implement an infrastructure modelling and monitoring tool that can be used to help manage some of the inherent complexity in modern infrastructure. We will attempt to design an infrastructure modelling language, and use this model to validate real-world systems, as well as generating helpful architecture diagrams for documentation purposes.

\chapter*{Originality Avowal}
I verify that I am the sole author of this report, except where explicitly stated to the contrary.

I grant the right to King’s College London to make paper and electronic copies of the submitted work for purposes of marking, plagiarism detection and archival, and to upload a copy of the work to Turnitin or another trusted plagiarism detection service. I confirm this report does not exceed 25,000 words.

@@

I would like to express my gratitude to Dr.\ Steffen Zschaler, for agreeing to supervise this project when it was a rather abstract idea. His subsequent useful advice throughout the year has also been invaluable.

@@

\subsection{Unit and Integration Testing}

@@

\begin{listing}[H]
\begin{minted}[fontfamily=fi4]{ruby}
class sshd {
    package { 'openssh-server':
        ensure => latest
    }
    service { 'ssh':
        subscribe => File[sshdconfig],
        require   => Package['openssh-server'],
    }
    file { 'sshdconfig': 
        name    => '/etc/ssh/sshd_config',
        owner   => root,
        group   => root,
        mode    => 644,
        source  => 'puppet:///sshd/sshd_config',
        require => Package['openssh-server'],
    }
}
\end{minted}
\caption{A puppet recipe snippet, declaratively configuring the SSH service on a host. The execution of this description is idempotent, so can be repeated safely to ensure convergence.}
\label{fig:PuppetDSLSnippet}
\end{listing}

@@

Whilst New Relic is simple to set up and provides a fairly deep insight into application performance, it is a relatively expensive service beyond a trivial number of hosts and severely lacks the extensibility of the open source solutions when it comes to monitoring other non-supported parts of the stack.

@@

\pagebreak
\chapter{Appendix}
\section{Service Specification Examples}
\label{dslexamples}

\subsection{X-Time}
\label{dslgem}
\inputminted[fontfamily=fi4]{ruby}{appendices/x-time.rb}

\subsection{X-Awards Site}
\inputminted[fontfamily=fi4]{ruby}{appendices/x-awards-site.rb}

\subsection{Workspace +}
\inputminted[fontfamily=fi4]{ruby}{appendices/workspace.rb}
